fairmetrics: An R package for group fairness evaluation

### 2025-06-05 utils/joss_paper/paper.Rmd
editing title per JOSS reviewer comments

---
title: '{fairmetrics}: An R package for group fairness evaluation'
tags:
  - R
  - Fairness
  - Machine Learning
  - Software
authors:
  - name: Benjamin Smith
    orcid: 0009-0007-2206-0177
    affiliation: 1
  - name: Jianhui Gao
    orcid: 0000-0003-0915-1473
    affiliation: 1
  - name: Jessica Gronsbell
    orcid: 0000-0002-5360-5869
    affiliation: 1
affiliations:
  - name: "Department of Statistical Science, University of Toronto"
    index: 1
date: "2025-06-02"
bibliography: paper.bib
output:
  rticles::joss_article
  #rticles::arxiv_article
  # md_document:
  #   preserve_yaml: TRUE
  #   variant: "markdown_strict"
journal: JOSS
---

>>>>

---
title: 'fairmetrics: An R package for group fairness evaluation'
tags:
  - R
  - Fairness
  - Machine Learning
  - Software
authors:
  - name: Benjamin Smith
    orcid: 0009-0007-2206-0177
    affiliation: 1
  - name: Jianhui Gao
    orcid: 0000-0003-0915-1473
    affiliation: 1
  - name: Jessica Gronsbell
    orcid: 0000-0002-5360-5869
    affiliation: 1
affiliations:
  - name: "Department of Statistical Science, University of Toronto"
    index: 1
date: "2025-06-02"
bibliography: paper.bib
output:
  rticles::joss_article
  #rticles::arxiv_article
  # md_document:
  #   preserve_yaml: TRUE
  #   variant: "markdown_strict"
journal: JOSS
---
